New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2023-01-13 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit paper

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

main <-
  left_join(main, df_merge,
            by = "ID")

@@

## Theoretical Backround

### Stress in Teaching Profession

@@

### Heart rate as an indicator for stress or arousal
Heart rate is physiologically regulated by the autonomic nervous system. An increase in the activity of the sympathetic as part of the autonomic nervous system results in the heart rate being speeded up ("fight or flight"). On the other hand, an increased activity of the parasympathetic as the counterpart has the effect of slowing down the heart rate ("rest and digest") [@Battipaglia2015]. In addition to the autonomic nervous system and genetic factors, heart rate is influenced by numerous external factors such as social, personal, psychological, environmental and behavioural factors [@wang2022using].

### Wrist-worn devices as a new approach to assess physiological measures

@@

XXX Helsinki XXX All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University. All participants were informed in detail about the aim and intention of the study prior to testing. Participation in the study was voluntary and only took place after written consent has been given.

@@

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

### Heart rate data

All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.

### Teachers' self-reported data of arousal during the teaching phase

@@

# Discussion and implications
The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
# bookdown::word_document2 
---

@@

# main <-
#   left_join(main, df_merge,
#             by = "ID")

@@

# Theoretical Background

## Stress in Teaching Profession

@@

## Heart rate as an indicator for stress or arousal
Heart rate is physiologically regulated by the autonomic nervous system. An increase in the activity of the sympathetic as part of the autonomic nervous system results in the heart rate being speeded up ("fight or flight"). On the other hand, an increased activity of the parasympathetic as the counterpart has the effect of slowing down the heart rate ("rest and digest") [@Battipaglia2015]. In addition to the autonomic nervous system and genetic factors, heart rate is influenced by numerous external factors such as social, personal, psychological, environmental and behavioural factors [@wang2022using].

## Wrist-worn devices as a new approach to assess physiological measures

@@

All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board and the authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University. All participants were informed in detail about the aim and intention of the study prior to testing. Participation in the study was voluntary and only took place after written consent has been given.

@@

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio [palmeri2020]. An alpha level of 0.05 was used for the statistical tests.

### Descriptive statistics

Means, standard deviations and the range of teachers’ heart rate and the self-reported data are shown in Table 2.

```{r descriptive statistics}
# Mean, SD and range for overall 
descrip_hr_overall <- main %>%
  filter(time_span %in% c("overall")) %>% 
  summarise("M heart rate in bpm" = round(mean(heart_rate),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate),
                                      digits = 2),
            "Min heart rate in bpm" = min(heart_rate),
            "Max heart rate in bpm" = max(heart_rate)
  )

# Mean, SD and range for individual phases 
descrip_hr_phases <- main %>% 
  filter(!time_span %in% c("overall")) %>% 
  group_by(time_span) %>% 
  summarise("M heart rate in bpm" = round(mean(heart_rate),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate),
                                      digits = 2),
            "Min heart rate in bpm" = min(heart_rate),
            "Max heart rate in bpm" = max(heart_rate)
  )

# # format and insert table in manuscript
# descrip_hr_phases %>%
# papaja::apa_table(
#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
#   )

# Mean, SD and range for disruption and confident factor
rating_table <- 
  df_rating %>% 
  filter(!is.na(confident_factor),
         !is.na(disruption_factor)) %>% 
   summarise("M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confident factor" = round(mean(confident_factor),
                                     digits = 2),
            "SD confident factor" = round(sd(confident_factor),
                                      digits = 2),
            "Min confident factor" = min(confident_factor),
            "Max confident factor" = max(confident_factor)
            )

Teachers’ average heart rate during the entire course of the study was approximately `r descrip_hr_overall %>% pull("M heart rate in bpm")` bpm with a standard deviation of `r descrip_hr_overall %>% pull("SD heart rate in bpm")` and a range from `r descrip_hr_overall %>% pull("Min heart rate in bpm")` to `r descrip_hr_overall %>% pull("Max heart rate in bpm")` bpm.

Means, standard deviations and the range of teachers’ heart rate for the different phases and the self-reported data are shown in Table 2.

### Multilevel regressions

@@

# Discussion and implications

### 2023-01-13 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
update fitbit paper

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

@@

To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings (Ertzberger \& Martin, 2016; Lowe, 2016). Runge et al. (n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate indicate more stress in teachers.

Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, inexpensive, and robust measurement method for assessing teachers' experience of arousal during teaching.

\hypertarget{theoretical-backround}{%
\subsection{Theoretical Backround}\label{theoretical-backround}}

\hypertarget{stress-in-teaching-profession}{%
\subsubsection{Stress in Teaching Profession}\label{stress-in-teaching-profession}}

@@

--\textgreater{} wie entsteht Stress
--\textgreater{} wie wurde Stress bisher gemessen

\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
\subsubsection{Heart rate as an indicator for stress or arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}

@@

\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
\subsubsection{Wrist-worn devices as a new approach to assess physiological measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}

@@

\hypertarget{teachers-self-assessment-of-arousal-during-the-teaching-phase}{%
\subsubsection{Teachers' self-assessment of arousal during the teaching phase}\label{teachers-self-assessment-of-arousal-during-the-teaching-phase}}

The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson. For this purpose, two numerical 11-point rating scales were used: \emph{(1)} The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: ``On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive'' \emph{(2)} The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: ``How confident did you feel in dealing with this event on a scale of 0-10? 0 is not confident at all and 10 is extremely confident''
The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable (Döring \& Bortz, 2016; Eid, Gollwitzer, \& Schmitt, 2015). The gradations of the rating scale were unambiguous and the intervals between them identical. The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.

@@

For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest. To ensure that the intervals are comparable for all participants, we decided on 10-minute intervals because this was the minimum duration of all intervals. The individual intervals are described in detail below.

\emph{(1)} The \emph{pre-teaching phase} was the first 10 minutes belonging to the interval of interest. This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors. After the experimenter briefly explained the project and the procedure of the study to the subject, contact details were subsequently collected as part of the hygiene concept of COVID-19 and the written consent to voluntarily participate in the study was requested. Next, the subject was asked to prepare the necessary materials for the lesson (connecting the laptop to the beamer, preparing worksheets, etc.). This phase varied in duration according to the prepared lesson (about 1-5min on average).

@@

Time management was regulated by the experimenter by showing time cards (yellow = 1 minute until the end; red = end of the lesson). The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants. XXX GENAUEN M + SD BERECHNEN XXX At the end of the lesson, the experimenter again noted the time and the steps on the clock.

\emph{(3)} The noted time of the lesson end was also the starting point for the \emph{post-teaching} phase as the third 10 minute interval. At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside. The letter search as a control condition was part of another project, which is why it will not be discussed further in the study. Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree; EMU, Helmke et al. (2014)) via the online survey website SoSci Survey. The completion of the questionnaire took approximately 5 minutes.

@@

\emph{(4)} The fourth 10 minute interval of interest was the \emph{interview phase} that are 10 minutes in the middle of the interview. To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch. This duration was divided in two to get to the middle of the interval. Then, 5 minutes were subtracted to get to the start of the 10-minute interval.

@@

\emph{(5)} The last interesting interval for the analyses is the \emph{end phase}, which was the 10 minutes before the subject took off the watch. In this interval, the subject answered a second questionnaire (Situational Judgment Test, Gold and Holodynski (2015)) to assess the subject's strategic knowledge of classroom management. The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades. Data from the questionnaire were again collected as an online questionnaire via the website www.soscisurvey.de and lasted approximately 10-15 minutes.

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses.

\hypertarget{heart-rate-data}{%
\subsubsection{Heart rate Data}\label{heart-rate-data}}

All participants were given a FitBit Smart Watch Charge 4 to wear during the experiment.

\hypertarget{rating-scale-data}{%
\subsubsection{Rating Scale Data}\label{rating-scale-data}}

@@

\hypertarget{discussion-and-implication}{%
\section{Discussion and implication}\label{discussion-and-implication}}

The analyses showed that wrist-worn fitness trackers are a suitable method to measure different phases of arousal in (prospective) teachers in laboratory settings, with clear effects visible even in intervals of just 10 minutes.

@@

@@

@@

>>>>

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.

XXX In this proof-of-concept study, we aimed to advance the field of teacher stress by collecting heart rate data with wrist-worn devices and testing a methodology that has the potential to provide more insights on the non-invasive assessment of teacher stress. XXX
}

@@

To date, there is still little evidence on the usefulness of heart rate measurements using fitness trackers in teaching and learning settings (Ertzberger \& Martin, 2016; Lowe, 2016). Runge et al. (n.d.) alone examined teacher stress in a relatively small sample (\emph{N} = 4 teachers) and showed that high heart rate indicates more stress in teachers.

Thus, there remains a lack of robust studies on whether fitness trackers are an efficient, low-cost, and robust measurement method for assessing teachers' experience of arousal during teaching.

\hypertarget{theoretical-background}{%
\section{Theoretical Background}\label{theoretical-background}}

\hypertarget{stress-in-teaching-profession}{%
\subsection{Stress in Teaching Profession}\label{stress-in-teaching-profession}}

@@

--\textgreater{} wie entsteht Stress

--\textgreater{} wie wurde Stress bisher gemessen

\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
\subsection{Heart rate as an indicator for stress or arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}

@@

\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
\subsection{Wrist-worn devices as a new approach to assess physiological measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}

Fuller et al. (2020) showed in their review article that wearable devices such as Fitbit watches are accurate and reliable for measuring heart rate in controlled settings.

@@

\hypertarget{teachers-self-reported-data-of-arousal-during-the-teaching-phase}{%
\subsubsection{Teachers' self-reported data of arousal during the teaching phase}\label{teachers-self-reported-data-of-arousal-during-the-teaching-phase}}

The subject's self-reported data of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson. For this purpose, two numerical 11-point rating scales were used: \emph{(1)} The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption (``On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive'') \emph{(2)} The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson (``How confident did you feel in dealing with this event on a scale of 0-10? 0 is not confident at all and 10 is extremely confident'').

The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjects' self-report and emotional experience, and thus to make them measurable and comparable (Döring \& Bortz, 2016; Eid, Gollwitzer, \& Schmitt, 2015). The gradations of the rating scale were unambiguous and the intervals between them identical. The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.

@@

For analyzing the heart rate data, we focused on five 10-minute intervals of theoretical interest for multiple reason. First, 10 minutes was to the minimum duration of all intervals, so we wanted to ensure the comparability of the intervals for all participants. Second, Lu et al. (2008) confirmed in their study that 10-minute intervals are an useful duration for analyzing photoplethysmography (PPG) data. Third, other studies revealed that the first minutes of the lesson start are essential regarding teacher-student interaction (Claessens et al., 2017; Donker, Van Gog, \& Mainhard, 2018).

The procedure of the study and how we calculated the five phases is described in the following:

\emph{(1)} The \emph{pre-teaching phase} was the first 10-minute interval of interest. This interval was calculated from the moment the subject arrived and the Fitbit watch was put on, which happened immediately after the subject was welcomed by the experimenter and the three actors. After the experimenter briefly explained the project and the procedure of the study to the subject, contact details were subsequently collected as part of the hygiene concept of COVID-19 and the written consent to voluntarily participate in the study was requested. Next, the subject was asked to prepare the necessary materials for the lesson (connecting the laptop to the beamer, preparing worksheets, etc.). This phase varied in duration according to the prepared lesson (about 1-5min on average).

@@

Time management was regulated by the experimenter by showing time cards (yellow = 1 minute until the end; red = end of the lesson). The lesson lasted about 18 minutes on average but only the first 10 minutes were used as an interval to ensure the identical duration for all participants. At the end of the lesson, the experimenter again noted the time and the steps on the clock.

\emph{(3)} The noted time of the lesson end was also the starting point for the \emph{post-teaching} phase as the third 10-minute interval. At the end of the lesson, the experimenter attached letters A through D in the lab while the teacher performed a second 9-point calibration outside. The letter search as a control condition was part of another project, which is why it will not be discussed further in the study. Subsequently, the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality (4-point Likert scale; 1 = strongly disagree; 2 = disagree; 3 = agree; 4 = strongly agree; EMU, Helmke et al. (2014)) via the online survey website SoSci Survey. The completion of the questionnaire took approximately 5 minutes.

@@

\emph{(4)} The fourth 10-minute interval of interest was the \emph{interview phase} that was 10 minutes in the middle of the interview. To ensure that all subjects were in the middle of the interview, we calculated the difference from the end of the lesson and from the time when the subject took off the watch. This duration was divided in two to get to the middle of the interval. Then, 5 minutes were subtracted to get to the start of the 10-minute interval.

@@

\emph{(5)} The last interesting interval for the analyses was the \emph{end phase}, which was the 10 minutes before the subject took off the watch. In this interval, the subject answered a second questionnaire (Situational Judgment Test, Gold and Holodynski (2015)) to assess the subject's strategic knowledge of classroom management. The subject was asked to judge alternative actions on school scenarios on a 6-point rating scale from 1 (A) to 6 (F) according to school grades. Data from the questionnaire were again collected as an online questionnaire via the website www.soscisurvey.de and lasted approximately 10-15 minutes.

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

\hypertarget{descriptive-statistics}{%
\subsubsection{Descriptive statistics}\label{descriptive-statistics}}

Means, standard deviations and the range of teachers' heart rate and the self-reported data are shown in Table 2.

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:descriptive statistics}Mean, SD and range for teachers' heart rate in individual phases}

\tiny{

\begin{tabular}{lllll}
\toprule
time\_span & \multicolumn{1}{c}{M heart rate in bpm} & \multicolumn{1}{c}{SD heart rate in bpm} & \multicolumn{1}{c}{Min heart rate in bpm} & \multicolumn{1}{c}{Max heart rate in bpm}\\
\midrule
after & 77.20 & 11.04 & 50.00 & 120.00\\
interview & 82.40 & 11.78 & 51.00 & 132.00\\
main & 100.28 & 16.55 & 56.00 & 164.00\\
pre & 96.21 & 14.10 & 56.00 & 139.00\\
subsequent & 94.08 & 14.28 & 63.00 & 150.00\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

Teachers' average heart rate during the entire course of the study was approximately 95.93 bpm with a standard deviation of 14.03 and a range from 56 to 139 bpm.

Means, standard deviations and the range of teachers' heart rate for the different phases and the self-reported data are shown in Table 2.

\hypertarget{multilevel-regressions}{%
\subsubsection{Multilevel regressions}\label{multilevel-regressions}}

@@

\hypertarget{discussion-and-implications}{%
\section{Discussion and implications}\label{discussion-and-implications}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-claessens2017positive}{}}%
Claessens, L. C., Tartwijk, J. van, Want, A. C. van der, Pennings, H. J., Verloop, N., Brok, P. J. den, \& Wubbels, T. (2017). Positive teacher--student relationships go beyond the classroom, problematic ones stay inside. \emph{The Journal of Educational Research}, \emph{110}(5), 478--493.

\leavevmode\vadjust pre{\hypertarget{ref-donker2018quantitative}{}}%
Donker, M. H., Van Gog, T., \& Mainhard, M. T. (2018). A quantitative exploration of two teachers with contrasting emotions: Intra-individual process analyses of physiology and interpersonal behavior. \emph{Frontline Learning Research}, \emph{6}(3), 162--184.

@@

\leavevmode\vadjust pre{\hypertarget{ref-fuller2020reliability}{}}%
Fuller, D., Colwell, E., Low, J., Orychock, K., Tobin, M. A., Simango, B., et al.others. (2020). Reliability and validity of commercially available wearable devices for measuring steps, energy expenditure, and heart rate: Systematic review. \emph{JMIR mHealth and uHealth}, \emph{8}(9), e18694.

@@

\leavevmode\vadjust pre{\hypertarget{ref-lu2008can}{}}%
Lu, S., Zhao, H., Ju, K., Shin, K., Lee, M., Shelley, K., \& Chon, K. H. (2008). Can photoplethysmography variability serve as an alternative approach to obtain heart rate variability information? \emph{Journal of Clinical Monitoring and Computing}, \emph{22}(1), 23--29.
